Transfer report

### 2019-01-12 Report/paper-all-data.Rmd
updates paper all data

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(knitr)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(xtable)
library(restimoter)

@@

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
estimote_pal_mono <- function(n){return(rep(estimote_pal[n],6))}
theme_set(theme_minimal())
```

@@

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(knitr)
library(dplyr)
library(reshape2)
library(broom)
library(brainvr.R)
library(xtable)
library(restimoter)
library(papaja)
library(googlesheets)

@@

source("helpers/block-t-test-improvement.R")
source("helpers/block-t-test.R")
source("helpers/block-measure.R")
source("helpers/block-correlation.R")

settings <- load_google_sheets()
df_participants <- settings$participants
df_participants <- df_participants %>% mutate(condition=paste0(First.phase,"-",Second.phase))
df_participants <- df_participants %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
overview <- settings$versions
overview <- overview %>% mutate(condition=paste0(First.phase,"-",Second.phase))
overview <- overview %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())

### Try running it without outliers
sub_walk_all[!is.na(sub_walk_all$norm_distance) & sub_walk_all$norm_distance > 3, c("distance", "min_norm_distance")] <- NA

condition_all_sums <- sub_walk_all %>% 
  group_by(exp_block_id, id, learning.condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

df_errors <- block_measure(condition_all_sums, "sum.errors")
df_distance <- block_measure(condition_all_sums, "mean.distance")

df_wide_errors <- dcast(condition_all_sums, learning.condition + id ~ exp_block_id, value.var = "sum.errors")
df_wide_distance <- dcast(condition_all_sums, learning.condition + id ~ exp_block_id, value.var = "mean.distance")
colnames(df_wide_errors) <- c("learning.condition","id","block1", "block2","block3","block4","block5","block6")
colnames(df_wide_distance) <- c("learning.condition","id","block1", "block2","block3","block4","block5","block6")
df_wide_errors$block34 <- (df_wide_errors$block3-df_wide_errors$block4)/(df_wide_errors$block3+df_wide_errors$block4)
df_wide_distance$block34 <- (df_wide_distance$block3-df_wide_distance$block4)/(df_wide_distance$block3+df_wide_distance$block4)

sub_walk_all_factor <- sub_walk_all
sub_walk_all_factor$exp_block_id <- factor(sub_walk_all_factor$exp_block_id)
sub_walk_all_factor$id <- factor(sub_walk_all_factor$id)
sub_walk_all_factor$learning.condition <- factor(sub_walk_all_factor$learning.condition)

knitr::opts_chunk$set(echo=F, warning = F, message = F)
```

@@

### Block 1-4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r, echo=F}
kable(block_t_test(sub_walk_all, 3, 1,"min_norm_distance"))
```
And for number of errors
```{r, echo=F}
kable(block_t_test(sub_walk_all, 3, 1,"errors"))
```
